---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spccharter

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/johnmackintosh/spccharter.svg?branch=master)](https://travis-ci.com/johnmackintosh/spccharter)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/johnmackintosh/spccharter?branch=master&svg=true)](https://ci.appveyor.com/project/johnmackintosh/spccharter)
[![R build status](https://github.com/johnmackintosh/spccharter/workflows/R-CMD-check/badge.svg)](https://github.com/johnmackintosh/spccharter/actions)
<!-- badges: end -->

The goal of spccharter is rapid analysis of multiple statistical process control charts.
The package will create, detect signals of improvement, and revise control limits.
Currently, 'C', 'P' and 'U' charts can be produced. 

## Installation

You cannot install the released version of spccharter from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("spccharter")
```

But the development version is available on [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("johnmackintosh/spccharter")
```
## Example

To follow:

```{r example, eval=FALSE}
library(spccharter)
spccharter(data, numerator = counts, datecol = date, 
           grpvar = category_1, plot_type = 'c', direction = "both")
```



